Nabi - A Preventative Solution Against JavaScript and Scriptless Tabnabbing Attacks

### 2015-05-05 paper/paper.tex
changes to results and intro

\section{Introduction}
\begin{comment}
The use of the internet has become an almost unavoidable part of life. As the internet becomes more involved with everyday life, users put more and more of their personal information online. Phishing is the process of stealing, gaining access to, or recording personal accounts or information. Phishing attacks try to convince the target to give up personal information such as passwords, account names, credit card numbers, addresses, and other valuable information or credentials. Phishing has many mediums such as email, phone, websites, and even mail. This information can be used in a variety of destructive ways from the thievery of personal assets to identity theft. Tabnabbing is a phishing technique that relies on the user’s trust of websites they have already viewed and considered safe. The site is changed to a malicious site when the user is not viewing the page. This is done using JavaScript to change the page while the tab is not in focus or by using the meta tag with a timer to redirect the page at a time when the user is most likely not viewing it. Phishing attacks are becoming more common as web use increases, and as users become more aware of phishing attacks, phishing techniques adapt to continue to be effective.
\end{comment}

@@

\section{Results}
The current build of Nabi restricts javascript from running in every tab the user has switched from. The tab is then refreshed to reflect those restrictions and to the cancel the actively running javascript on that page. The page that is switched to is given access to run javascript and is also refreshed to reflect the change in permissions. This prevents javascript in the unactive from running while the user is not viewing it, but allows it to reactivate once the user returns.

>>>>

\section{Introduction}
\begin{comment}
The use of the internet has become an almost unavoidable part of life. As the internet becomes more involved with everyday life, users put more and more of their personal information online. Phishing is the process of stealing, gaining access to, or recording personal accounts or information. Phishing attacks try to convince the target to give up personal information such as passwords, account names, credit card numbers, addresses, and other valuable information or credentials. Phishing has many mediums such as email, phone, websites, and even mail. This information can be used in a variety of destructive ways from the thievery of personal assets to identity theft. Tabnabbing is a specific phishing technique that relies on the user’s trust of websites they have already viewed and considered safe. Some users often leave many tabs open to return to interesting websites at a later time and this behavior makes those users the perfect target for this type of attack. When the user is not has left a tab a malicious webesite can detect that the user is not currently viewing that tab and change the content of that page. This is done using JavaScript or by using the meta tag with a timer to redirect the page at a time when the user is most likely not viewing it. An example of one such change is making the page apear to be the gmail login page in the hopes that the user will atempt to login giving the malicious site the username and password for the unsuspecting user. Phishing attacks are becoming more common as web use increases, and as users become more aware of phishing attacks, phishing techniques adapt to continue to be effective. Tabnabbing is one such new technique that has emerged recently and is effective even against users that have been trained to only give sensitive information to trusted websites.
\end{comment}

@@

\section{Results}
The current build of Nabi restricts javascript from running in every tab the user has switched from. The tab is then refreshed to reflect those restrictions and to the cancel the actively running javascript on that page. The page that is switched to is given access to run javascript and is also refreshed to reflect the change in permissions. This prevents javascript in the inactive tab from running while the user is not viewing it, but allows it to reactivate once the user returns. Because of this our strategy for defending against tabnabbing attacks allows the user to continue using the browser almost as if JavaScript has not been disabled.
